Network Visualizations in \MakeLowercase{\texttt{ggplot2}}

### 2015-10-13 inst/paper.Rnw
bike sharing example

\maketitle
\begin{abstract}
There are many implementations of static network visualization in R, but none are equipped with the flexibility and functionality of \texttt{ggplot2}.  \texttt{geom\_net} was created to fill this gap. Using two data frames to describe vertex and edge information, \texttt{geom\_net} makes use of the underlying structure of \texttt{ggplot2} to visualize networks. This makes it possible to easily facet networks according to covariates  or change aesthetics such as shape, size, or color according to additional edge or vertex information.
\end{abstract}
<<setup_knitr, echo=FALSE>>=
library(knitr)
opts_chunk$set(
  tidy = FALSE, echo=FALSE, cache=FALSE, eval = TRUE,
  message = FALSE, warning = FALSE,
  fig.height = 8, fig.width = 8, fig.align = 'center', fig.show='hide'
)
@

>>>>

\maketitle
\begin{abstract}
There are many implementations of static network visualization in R, but none are equipped with the flexibility and functionality of \texttt{ggplot2}.  \texttt{geom\_net} was created to fill this gap. Using two data frames to describe vertex and edge information, \texttt{geom\_net} makes use of the underlying structure of \texttt{ggplot2} to visualize networks. This makes it possible to easily facet networks according to covariates  or change aesthetics such as shape, size, or color according to additional edge or vertex information.
\end{abstract}
<<setup_knitr, echo=FALSE>>=
library(knitr)
opts_chunk$set(
  tidy = FALSE, echo=FALSE, cache=FALSE, eval = TRUE,
  message = FALSE, warning = FALSE, highlight = FALSE,
  fig.height = 8, fig.width = 8, fig.align = 'center', fig.show='hide'
)
@
